Stability and Performance of Coalitions of Prosumers Through Diversification in the Smart Grid

### 2015-11-05 Article.tex
update

This section provides most of the notations and introduces important concepts for the rest of the paper. We consider a set $ \mathcal{A} = \{a_{1},a_{2},...,a_{N} \} $ of N prosumers configured randomly, and for each agent, we simulate its extra-production $ P_{i}(t),\ \forall i \in \mathcal{A} $ from 2006 to 2012. Based on these historical values, our objective is now to form groups of prosumers so that the global power production resulting from the superposition of individual's extra-productions be both sufficiently high and predictable. Let $ P_{S}(t) = \sum_{i \in S} P_{i}(t) $ be the extra-production of coalition S at time t.

>>>>

This section provides most of the notations and introduces important concepts for the rest of the paper. We consider a set $ \mathcal{A} = \{a_{1},a_{2},...,a_{N} \} $ of N prosumers of the distribution network. Each agent is configured randomly and we simulate its extra-production $ P_{i}(t),\ \forall i \in \mathcal{A} $ from 2006 to 2012. Based on these historical values, our objective is now to form groups of prosumers so that the global power production resulting from the superposition of individual's extra-productions be both sufficiently high and predictable. Let $ P_{S}(t) = \sum_{i \in S} P_{i}(t) $ be the extra-production of coalition S at time t.
